\documentclass[10pt,a4paper,twocolumn,twoside]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{times}
\usepackage{titlesec}
\usepackage{multirow}
\usepackage{lettrine}
\usepackage{pdflscape}
\usepackage[edges]{forest}
\usepackage{url}
\usepackage[top=2cm, bottom=1.5cm, left=2cm, right=2cm]{geometry}
\usepackage[figurename=Fig.,tablename=TAULA]{caption}
\captionsetup[table]{textfont=sc}

\author{\LARGE\sffamily Segovia Barreales, Richard}
\title{\Huge{\sffamily Reducing dizziness when using a video-see-through head-mounted display}}
\date{}

\newcommand\blfootnote[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}%
  \addtocounter{footnote}{-1}%
  \endgroup
}

%
%\large\bfseries\sffamily
\titleformat{\section}
{\large\sffamily\scshape\bfseries}
{\textbf{\thesection}}{1em}{}

\begin{document}

\fancyhead[LO]{\scriptsize AUTHOR: SEGOVIA BARREALES, RICHARD}
\fancyhead[RO]{\thepage}
\fancyhead[LE]{\thepage}
\fancyhead[RE]{\scriptsize EE/UAB TFG INFORMÀTICA: REDUCING DIZZINESS WHEN USING A VIDEO-SEE-THROUGH HEAD-MOUNTED DISPLAY}

\fancyfoot[CO,CE]{}

\fancypagestyle{primerapagina}
{
   \fancyhf{}
   \fancyhead[L]{\scriptsize TFG EN ENGINYERIA INFORMÀTICA, ESCOLA D'ENGINYERIA (EE), UNIVERSITAT AUTÒNOMA DE BARCELONA (UAB)}
   \fancyfoot[C]{\scriptsize March 2018, Escola d'Enginyeria (UAB)}
}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\pagestyle{fancy}

\maketitle

\thispagestyle{primerapagina}


\blfootnote{$\bullet$ E-mail: richard.segovia@e-campus.uab.cat}
\blfootnote{$\bullet$ Menció en Computació}
\blfootnote{$\bullet$ Project supervised by: Coen Antens (CVC) and Felipe Lumbreras (Computació)}
\blfootnote{$\bullet$ Course 2017/18}

\section{Introduction}


\section{Objectives}
%- Se habia infraestimado el tiempo de desarrollo de la parte del calculo de la vergencia como veremos en planning
%- esto obliga al retraso y a la replanificacion del projecto
%- se introduce como objetivo tener un sistema de calibracion compatible con la interfaz del visor especificacion!

After these firsts weeks of development some objectives have change and other have appeared, as we will explain in section \ref{sec:planning} the development time of the depth map was underestimated and some change had to be made in the project planning.

Related with the depth map, a new objective appeared, the integration of a calibration system that will allow us to undistort the stereo image pair. The integration of this system is now mandatory because undistorted images are required in order to obtain a reliable depth map.

Also after the development of the depth map a issue appeared, the speed of the generation of depth map images was far from real time, this could give our system a huge latency, preventing any dizziness improvement or real scenario uses. For that reason, the improvement of this speed will be a new objective.


\section{Methodology}
%- se han ido utilizando las herramientas descritas en la primera parte, trello, github
%se utiliza opencv para el calculo de la calibracion
%se ha ido documentando cada parte del funcionamiento
% utilizar libelas openmp?
The custom scrum methodology explained in the previous report has been followed without any change. Evey part of the development process has been documented and every change in the code has been uploaded to a github repository. The OpenCV \cite{web:opencv} library has been used to develop the calibration and undistort phase. 


\section{Planning and development progress}
\label{sec:planning}

%- En el momento de la integracion y utilizacion de la libreria libelas nos dimos cuenta de que era necesaria tambien la integracion de un sistema de calibracion de las camaras que nos permitiese obtener el undistort de las imagenes para que el par stereo estuviese perfectamente alineado. Esto supuso un retraso en el desarrollo, ademas la libreria libelas necesito ciertas modificaciones para conseguir que funcionase correctamente. 
%
%- muy sensible a la calibracion! problema fisico! se da a conocer a los compañeros que estan trabajando con los prototipos
%
%- lentitud de ejecucion de libelas -> reducir tamaño de la imagen captada
%								   -> utilizar libreria libelas openmp?
%								   -> poner tabla
%- presets echos (?) pero no testeados con usuarios
%- las pruebas con usuarios tambien se han retrasado pero ya se estan diseñando(explicar)
%- se ha utilizado opencv en c para implementar la calibracion de las camaras(se introduce y se realiza este objetivo)
% 

\begin{itemize}
	\item Reduction of the image resolution: In our use case, only the center of the images is necesary, this is because it is where the user will be usually looking at, therefore taking off the outer pixels of the images will not alter the behavior of the vergence system and will improve the speed of the generation of depth map images.
\end{itemize}

\section{Acknowledgment}
This work is supported in part by a CVC transfer project with ProCare Light company, and partially funded by the Spanish Ministry of Economy and Competitiveness and FEDER under grants TIN2014-56919-C3-2-R and TIN2017-89723-P.

\bibliography{biblio}
\bibliographystyle{plain}

\appendix



\end{document}

